Predict Models

### 2024-01-22 scripts/generate_RF_models.Rmd
perform rfe to subset predictors to reasonable size for prediction onto a gridded surface incroporated into modeller
ran all models

p <- '/media/steppe/hdd/Geospatial_data/WesternPlantPredictors2'
paths <- list.dirs(p, recursive = T)
paths <- paths[2:length(paths)]
paths <- paths[! grepl('chelsa$|veg_cover$|soilgrids$|sand$|silt$|clay$|phh2o$|cfvo$|soc$', paths) ]

@@

cores <- parallel::detectCores()
lapply(splicies[3:335], modeller)

>>>>

p <- '~/Documents/WesternPlantPredictors2'
paths <- list.dirs(p, recursive = T)
paths <- paths[2:length(paths)]
paths <- paths[! grepl('chelsa$|veg_cover$|soilgrids$|sand$|silt$|clay$|phh2o$|cfvo$|soc$', paths) ]

@@

cores <- parallel::detectCores()
lapply(splicies, modeller, suffix = '1k')

### 2024-01-22 scripts/predict_models.Rmd
ran all models

# unix::rlimit_as(1e32)
# setGDALconfig(c("GDAL_MAX_DATASET_POOL_SIZE"), c(""))
```

@@

pmodels <- '../results/rf_models'
f <- file.path(pmodels, list.files(pmodels))
f <- data.frame(
  path = f,  
  species = gsub('-.*$', '', basename(f)), 
  time = gsub('[A-Za-z]', '', basename(f))
  ) |>
  mutate(time = gsub('_-|[.]', '', time),
         time = gsub('_', ' ', time), 
         time = as.POSIXct(time)) |>
  group_by(species) |>
  slice_max(order_by = time, n = 1) |>
  pull(path)

@@

@@

lapply(models_occ[30:335], predict_wrapper)

>>>>

setGDALconfig('GDAL_MAX_DATASET_POOL_SIZE=1024')
```

@@

pmodels <- '../results/rf_models'
f <- file.path(pmodels, list.files(pmodels))
f <- data.frame(
  path = f,  
  species = gsub('-.*$', '', basename(f)), 
  time = gsub('[A-Za-z]', '', basename(f))
  ) |>
  mutate(time = gsub('_-|[.]', '', time),
         time = gsub('_', ' ', time), 
         time = trimws(time),
         time = gsub('^.1-|^1-', '', time), 
         time = as.POSIXct(time)) |>
 # group_by(species) |>
  filter(str_detect(species, '1k$')) |>
 # slice_max(order_by = time, n = 1) #|>
  pull(path)

@@

   terra::tmpFiles(current = FALSE, orphan = TRUE, old = TRUE, remove = TRUE)

@@

lapply(models_occ[68:335], predict_wrapper)
